---
title: "Developing Data Products - Week 4 Assignment"
author: "Santanu Dey"
date: "12 September 2017"
output: slidy_presentation
---

# Shiny Application and Reproducible Pitch

```{r}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

 - This presentation is the first part of the assignment of week 4, ***Developing Data Products course from Coursera***(<https://www.coursera.org/learn/data-products>).
 
 - The presentation contains information about the second part of the above mentioned assignment.

## Application

 - The second part of the mentioned assignment was to develop a web application. The application was named ***MPG Prediction***. An instance is up & running at <https://deysantanu84.shinyapps.io/DDP_Week4Assignment/>.
 
 - In the application, a prediction model is generated, based on a car parameters dataset (HP, weight, gears, etc.). Then, a user can play freely with the UI values in order to simulate the parameters of an hypothetical car and be able to predict its MPG consumption.
  
## Dataset

Dataset used by the application is the [Motor Trend Car Road Tests](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html) (from now on *'mtcars'*). The data was extracted from the ***1974 Motor Trend*** US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

Next, the dataset structure: 

```{r cars, echo = TRUE}
str(mtcars)
```

## Prediction

A Random Forest prediction model is generated and trained using the *'mtcars'* dataset. The goal of this model is to predict the fuel consumption (***mpg*** variable) based on the rest of the variables:

```{r echo = FALSE}
suppressWarnings(suppressMessages(library(caret)))
suppressWarnings(suppressMessages(library(randomForest)))
set.seed(553311)
```

```{r echo = TRUE}
customTrainControl <- trainControl(method = "cv", number = 10)
carsRandomForestModelBuilder <- function() {
    return(
        train(
            mpg ~ ., 
            data = mtcars,
            method = "rf",
            trControl = customTrainControl
        )
    )
}

carsRandomForestModelBuilder()
```
